### 2016-07-28 Chapters/Ch04-PaperSummary.tex
Not much...

@@

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/algorithm.tikz}}
\caption{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2O\_MEP-diff-pcmdc-dc}
\caption{\ce{H2O}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Odiff_pcmdc-dc}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2Po\_MEP-diff-pcmdc-dc}
\caption{\ce{H2Po}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Podiff_pcmdc-dc}
\end{subfigure}
\caption{
  \todo[inline]{Recalculate MEP maps and reobtain these plots using ParaView.}
  Molecular electrostatic potential (\acs{MEP}) maps for \ce{H2O} and \ce{H2Po} at
  the \acs{DFT}/PBE0 level of theory.
  The isocontours are in the range $[-0.02, 0.02] \si{\hartree\per\elementarycharge}$ and are
  color-coded from red to blue.
  The values plotted are differences between the values obtained for the
  Hamiltonians referred to in the subcaptions. The geometry optimized \emph{in
  vacuo}, using the \acl{DC} Hamiltonian as reference.
  \acs{PCM}-\acs{DC}: \acl{DC} in water, \acs{DC}: \acl{DC} \emph{in vacuo}.}
\label{fig:MEP_maps}
\end{figure}

>>>>

\epigraph{$\frac{1}{2}$ research and $\frac{1}{2}\,\,T\acute{\epsilon}\chi\nu\eta$

          $\frac{1}{2}$ observation, $\frac{1}{2}\,\,T\acute{\epsilon}\chi\nu\eta$

          $\frac{1}{2}$ training, $\frac{1}{2}\,\,T\acute{\epsilon}\chi\nu\eta$}{
  --- \textsc{Ezra Pound}, \textit{Canto LXXXV}}

@@

\begin{figure}[!htb]
\centering
\scalebox{0.8}{\input{gfx/algorithm.tikz}}
\caption[Modular approach to programming a \acs{PCM} functionality into an existing \acs{SCF} code.]{
  Schematic view of the implemented SCF algorithm. Computations/data in
  \textcolor{Blue}{blue} are on the \pcmsolver side, in
  \textcolor{Green}{green} on the \DIRAC side.
  }
\label{fig:algorithm}
\end{figure}

\todo[inline]{Recalculate MEP maps and reobtain these plots using ParaView.}
\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2O\_MEP-diff-pcmdc-dc}
\caption{\ce{H2O}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Odiff_pcmdc-dc}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\missingfigure{Reobtain this figure: H2Po\_MEP-diff-pcmdc-dc}
\caption{\ce{H2Po}: $\mathrm{MEP}_\mathrm{PCM-DC} - \mathrm{MEP}_\mathrm{DC}$}
\label{fig:H2Podiff_pcmdc-dc}
\end{subfigure}
\caption[Molecular electrostatic potential (\acs{MEP}) maps for \ce{H2O} and \ce{H2Po} at
  the \acs{DFT}/PBE0 level of theory.]{
  Molecular electrostatic potential (\acs{MEP}) maps for \ce{H2O} and \ce{H2Po} at
  the \acs{DFT}/PBE0 level of theory.
  The isocontours are in the range $[-0.02, 0.02] \si{\hartree\per\elementarycharge}$ and are
  color-coded from red to blue.
  The values plotted are differences between the values obtained for the
  Hamiltonians referred to in the subcaptions. The geometry optimized \emph{in
  vacuo}, using the \acl{DC} Hamiltonian as reference.
  \acs{PCM}-\acs{DC}: \acl{DC} in water, \acs{DC}: \acl{DC} \emph{in vacuo}.}
\label{fig:MEP_maps}
\end{figure}

### 2016-07-28 FrontBackmatter/Acknowledgments.tex
Add commands, fix notations
Not much...

\chapter*{Introduction}
\addtocontents{toc}{\protect\vspace{\beforebibskip}} % to have the bib a bit from the rest in the toc
\addcontentsline{toc}{section}{\tocEntry{Introduction}}

\epigraph{How does newness come into world? How is it born?

    Of what fusions, translations, conjoinings is it made?

    How does it survive, extreme and dangerous as it is? What compromises, what deals,
    what betrayals of its secret nature must it take to stave off the wrecking crew, the
    exterminating angel, the guillotine?

    Is birth always a fall?

    Do angels have wings? Can men fly?}{
    --- \textsc{Salman Rushdie}, \textit{The Satanic Verses}}

>>>>

%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

\epigraph{
Just a perfect day

You made me forget myself

I thought I was

Someone else, someone good}{
--- \textsc{Lou Reed}}

\endgroup

### 2016-07-28 FrontBackmatter/Introduction.tex
Not much...

\epigraph{How does newness come into world? How is it born?

    Of what fusions, translations, conjoinings is it made?

    How does it survive, extreme and dangerous as it is? What compromises, what deals,
    what betrayals of its secret nature must it take to stave off the wrecking crew, the
    exterminating angel, the guillotine?

    Is birth always a fall?

    Do angels have wings? Can men fly?}{
    --- \textsc{Salman Rushdie}, \textit{The Satanic Verses}}

>>>>

\epigraph{
pity this busy monster, manunkind,
    }{
    --- \textsc{E. E. Cummings}}
